---
title: "A spatial Analysis of New York Evictions"
Author: Mingyuan Zhao | 
Student Number: 23134046
output: html_document
date: "`r format(Sys.time(), '%X, %d %B, %Y')`"
---
# Originality declaration  

I, [Mingyuan Zhao], confirm that the work presented in this assessment is my own. Where information has been derived from other sources, I confirm that this has been indicated in the work.

date: `r format(Sys.time(), '%d %B, %Y')`

# Start your response here

## Initial project scope

* What is my research question - is it different to the set question and why

> This research will identify the spatial patterns that can be used to help preventing people being evicted in the New York.

> My question is "are the evicitions in 2020 for New York showing a certain spatial pattern? Are they spatially random or clustering?"

> A question for Spatial autocorrelation..."are the densitites of evicitions in New York similar over community districts for 2020"

> A question for spatial regression..."What are the factors that might lead to variation in evictions across New York in 2020?"

* Is it appropriate to use 2020 as a year? 

> It is necessart to use year 2020, 2021 and 2022 as the study years. Because we can see the differences between years.


####################### Loading Data ###############################
```{r}
# library packages
library(spatstat)
library(here)
library(sp)
library(rgeos)
library(maptools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)
library(stringr)
library(janitor)
library(tidyverse)
```
> Library packages for further analysis. 


```{r}
# reading data
# CRS: 27700
evictions <- read.csv(here::here(
  "practical exam 1", "Evictions_20231118.csv"),
                     na = c("NA", "n/a"))

Borough <- st_read(here::here(
  "practical exam 1", "Community Districts",
  "geo_export_10e2af58-06db-468f-8ff7-a9572bee0603.shp"))%>%
  st_transform(., 6538)

qtm(Borough)
```
> 

######################### Cleaning Data ##############################
```{r}
# summary data
colnames(evictions)
```

```{r}
summary(evictions)
```

```{r}
summary(Borough)
```

```{r}
# converting the data type
evictions$Date <- as.Date(evictions$Executed.Date, format = "%m/%d/%Y")

# Selecting data from evictions
evictionNew <- evictions %>%
   dplyr::filter(str_detect(Date, "2020")) %>%
   filter(!is.na(Longitude)) %>%
   filter(!is.na(Latitude)) %>%
   filter(str_detect(Residential.Commercial, "Residential"))
```
> Select data from 2020-01-01 to 2020-12-30
> Focus on the Residental area

########################## Joining Data ##############################
```{r}
# change csv into spatial points
sf_points <- evictionNew %>%
  st_as_sf(., coords = c("Longitude", "Latitude"),
           crs = 4326)%>%
  st_transform(., crs=6538)
    

qtm(sf_points)
```


```{r}
st_crs(sf_points)
```

```{r}
st_crs(Borough)
```

```{r}
# Spatial subsetting
Sub_points <- sf_points[Borough, , op = st_within]


# plot the evictions in the city
tmap_mode("plot")
tm_shape(Borough) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(sf_points) +
  tm_dots(col = "blue")
```

########################## Point pattern analysis ###############################
```{r}
#create a sp object
Sub_points <- Sub_points %>%
  as(., 'Spatial')

#now set a window as the borough boundary
window <- as.owin(Borough)
plot(window)

#create a ppp object
Sub_points.ppp <- ppp(x=Sub_points@coords[,1],
                          y=Sub_points@coords[,2],
                          window=window)

Sub_points.ppp %>%
  plot(.,pch=16,cex=0.5, 
       main="Sub Points Harrow")

# Kernel Density Estimation
Sub_points.ppp %>%
  density(., sigma=500) %>%
  plot()

```

############ Density-based spatial clustering of applications ############
```{r}
K <- Sub_points.ppp %>%
  Kest(., correction="border")%>%
  plot()
```
###################### DBSCAN Analysis ###########################

```{r}
library(fpc)
#first check the coordinate reference system of the spatial polygon:
st_geometry(Borough)
```
```{r}
install.packages(FNN)
library(FNN)  # 加载 FNN 包
k_distance <- knn.dist(your_data, k = k_value)

```


```{r}
#first extract the points from the spatial points data frame
 DBdataframe <- Sub_points %>%
  coordinates(.)%>%
  as.data.frame()

#now run the dbscan analysis
db <- DBdataframe %>%
  fpc::dbscan(.,eps = 1000, MinPts = 60)

#now plot the results
plot(db, DBdataframe, main = "DBSCAN Output", frame = F)
plot(Borough$boro_cd, add=T)
```

